### 2025-06-07 project_Omar/paper.tex
bibtex issues. Maybe minor corrections

% detector de pixeles

During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \~ 0.5$, against an average of 57 in recent physics runs. The data is then distributed in 32 different datasets of events. %referencia pa la imagen de pile-up en runs de fisica

@@

% a couple graphs, maybe??

>>>>

% vdm graph

During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \approx 0.5$, against an average of 57 in recent physics runs. The data is then distributed in 32 different datasets of events. %referencia pa la imagen de pile-up en runs de fisica

@@
